---
title: "Meta-analysis: Toy Preferences in Children"
author: "Your Name"
format: html
execute:
  echo: true
---

```{r setup, include=FALSE}
library(meta)
library(readxl)
library(dplyr)
```

## Load and Prepare Data

```{r}
data <- read_excel("data/metaanalysis_data.xlsx")

meta_model <- metacont(
  n.e = data$N_boys,
  mean.e = data$Mean_boys_play_male,
  sd.e = data$SD_boys_play_male,
  n.c = data$N_girls,
  mean.c = data$Mean_girls_play_male,
  sd.c = data$SD_girls_play_male,
  data = data,
  studlab = data$Study,
  sm = "SMD",
  common = TRUE,
  random = TRUE,
  method.random.ci = "HK"
)
```

## Forest Plot

```{r}
forest(meta_model)
```

## Funnel Plot

```{r}
funnel(meta_model, main = "Funnel Plot (Publication Bias Check)")
```

## Meta-regression: Study Design & Country

```{r}
# Rename and convert quality/method columns
data <- data %>%
  rename(
    Neutral_toys = `Neutral toys`,
    Parent_present = `Parent present`
  )

data$Neutral_toys <- as.factor(data$Neutral_toys)
data$Parent_present <- as.factor(data$Parent_present)

metareg(x=meta_model, ~ Neutral_toys + Parent_present + Setting + Country, data = data)
```

## Meta-regression: Author Gender

```{r}
data$Author_female_ratio <- data$`Female authors` / (data$`Female authors` + data$`Male authors`)
metareg(x=meta_model, ~ Author_female_ratio, data = data)
```

## Conclusion

- The overall effect size suggests boys spend more time playing with male-typed toys than girls.
- The funnel plot indicates possible bias (or not).
- Factors like parent presence, toy neutrality, and gender equality (Country) may influence the result.
- Author gender distribution might also correlate with effect size.
